Classical mechanics and infinitesimal reducibility

### 2021-10-10 Overviews/Classical mechanics/ClassicalMechanicsOverview.tex
Overviews: updating revtex4 reference
Overviews: classical mechanics review

\title{Assumptions of Physics overview: \\
	Classical mechanics and infinitesimal reducibility }
\author{Gabriele Carcassi, Christine A. Aidala}
\affiliation{Physics Department, University of Michigan, Ann Arbor, MI 48109}

@@

\begin{abstract}
We briefly show how classical mechanics can be rederived and better understood as a consequence of three assumptions: infinitesimal reducibility, deterministic and reversible evolution, and kinematic equivalence. This work is an overview of some of the results of Assumptions of Physics, a project that aims to identify a handful of physical principles from which the basic laws can be rigorously derived  (\url{https://assumptionsofphysics.org}).
\end{abstract}

@@

The overall argument (see \cite{AoPPhy1,AoPBook} for more details) can be summed up in the following diagram that can be used as a guide throughout this note.

>>>>

\title{Classical mechanics and infinitesimal reducibility }
\author{Gabriele Carcassi, Christine A. Aidala}
\affiliation{Physics Department, University of Michigan, Ann Arbor, MI 48109}

@@

\begin{abstract}
We briefly show how classical mechanics can be rederived and better understood as a consequence of three assumptions: infinitesimal reducibility, deterministic and reversible evolution, and kinematic equivalence.
\end{abstract}

@@

The overall argument (see \cite{AoPPhy1,aop-book} for more details) can be summed up in the following diagram that can be used as a guide throughout this note.
